### 2014-09-06 relax2.tex
titles changed to value relaxation + path relaxation

\section{Exploration of Unexecuted Branches}~\label{sec:relax2}
We now switch to the second feature of \tool, which is to reason about 
neighboring executions involving unexecuted branches.
%in the original trace $\tau$.
At the high level, we enhance the constraints to model the unexecuted branches.
However to ensure soundness, we cannot encode the unexecuted branches as
normal static analyses do because they usually perform approximations such as bounded
loop unrolling and heap abstraction. The basic idea is to {\em only encode the
unexecuted branches when they can be precisely modeled based on our trace 
$\tau$.} 
%replace the constraints that model the executed branch to the constraints that conservatively model the possible executions in both branches.
%We leverage the static analysis to  realize this relaxation.

>>>>

\section{Path Relaxation}~\label{sec:relax2}
We now switch to the second feature of \tool, which is to reason about 
neighboring executions involving unexecuted branches.
%in the original trace $\tau$.
At the high level, we enhance the constraints to model the unexecuted branches.
However to ensure soundness, we cannot encode the unexecuted branches as
normal static analyses do because they usually perform approximations such as bounded
loop unrolling and heap abstraction. The basic idea is to {\em only encode the
unexecuted branches when they can be precisely modeled based on our trace 
$\tau$.} 
%replace the constraints that model the executed branch to the constraints that conservatively model the possible executions in both branches.
%We leverage the static analysis to  realize this relaxation.
